\textsc{Atomic modeling of argon}\\ \footnotesize{\textsc{Project 5 --- FYS3150}}

### 2015-11-28 projects/project_5/molecular_dynamics/article/article.tex
getting plots

\documentclass{article}
\usepackage[]{enumerate} 
\usepackage[]{graphicx} 
\usepackage[]{subcaption} 
\usepackage[]{amsthm, amsmath, amssymb} 
\usepackage[]{hyperref} 
\urlstyle{sf}
\graphicspath{{../pictures/}}

@@

\begin{document}
\maketitle    
\tableofcontents
\section{Introduction}
\label{sec:introduction}
    Molecular dynamics (referred to as MD), deals with the time evolution of a
    system of particles, typically atoms or molecules. Being first explored in
    the late 1950's, it has had a wide range of applications, in fields as
    materials science, biochemistry and biophysics. It is based on the simple
    idea of considering a finite number of molecules and letting them interact
    for a fixed amount of time, which gives us an idea of how the system
    evolves.

@@

    We are also interested in the instantaneous temperature of the system, and
    the equipartition theorem \cite{equipar} can help us with this. The theorem
    relates the average energy of a system to its temperaturkke and gives us the
    relation $\langle E_k \rangle = (3/2)k_bT$ which can be solved for
    temperature:
    \begin{equation}
        \notag
        T = \frac{2}{3} \frac{E_k}{nk_b}.
    \end{equation}
    Notice the removal of the brackets --- we are only interested in the
    \emph{instantaneous} temperature at any point in time. We also recall that
    since our units are scaled, Boltzmann's constant is equal to one.

@@

We initially decided to use the Velocity-Verlet integration method as opposed
to Euler-Cromer for its good energy conservation. We now simulate a set of
similar systems with varying temperature and look at how the fluctuations in
total energy scales with the timestep $\Delta T$. In order to do this we can
consider the standard-devation of the total energy.

>>>>

\documentclass[a4paper]{article}
\usepackage[]{enumerate} 
\usepackage[]{graphicx} 
\usepackage[]{subcaption} 
\usepackage[]{amsthm, amsmath, amssymb} 
\usepackage[]{fancyhdr}
\usepackage[]{hyperref} 
\urlstyle{sf}
\graphicspath{{../pictures/}}

@@

\begin{document}
\maketitle

\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{ch.pdf}
\end{figure}

\begin{abstract}
\end{abstract}
\tableofcontents
\section{Introduction}
\label{sec:introduction}
    Molecular dynamics (referred to as MD), deals with the time evolution of a
    system of particles, typically atoms or molecules. Being first explored in
    the late 1950's, it has had a wide range of applications, in fields as
    materials science, biochemistry and biophysics. It is based on the simple
    idea of considering a finite number of molecules and letting them interact
    for a fixed amount of time, which gives us an idea of how the system
    evolves.

@@

    We are also interested in the instantaneous temperature of the system, and
    the equipartition theorem \cite{equipar} can help us with this. The theorem
    relates the average energy of a system to its temperature and gives us the
    relation $\langle E_k \rangle = (3/2)k_bT$ which can be solved for
    temperature:
    \begin{equation}
        \notag
        T = \frac{2}{3} \frac{E_k}{nk_b}.
    \end{equation}
    Notice the removal of the brackets --- we are only interested in the
    \emph{instantaneous} temperature at any point in time. We also recall that
    since our units are scaled, Boltzmann's constant is equal to one.

@@

We initially decided to use the Velocity-Verlet integration method instead of
Euler-Cromer because of its good energy conservation. It is therefore of
interest to examine exactly what kind of impact this change of integration
method has for our simulations.  We now simulate a set of similar systems with
varying temperature and look at how the fluctuations in total energy scales
with the timestep $\Delta T$. In order to do this we can consider the
standard-devation of the total energy.
